### 2018-06-12 Shiva Dissertation/chap/conclusion.tex
Made few edits and added the new pictures.

 Today there are more robots than ever before.
 This dissertation provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.
 Our future goal is to perform assembly using particle swarms to manipulate and attach components. Future efforts should be directed toward examining the effects of Brownian noise, pose control for multiple-part assembly, trajectory prediction, and manipulation in crowded workspaces.
 We assumed friction was sufficient to completely stop particles in contact with the boundary. 
  The algorithms would require retooling to handle small friction coefficients.

>>>>

 Today there are more robots than ever before.
 This dissertation provides foundational algorithms and techniques for steering swarms, object manipulation, and addressing obstacle fields, but there are many opportunities to extend the work.
 Extensions to Chapter 2 and 3 is to perform assembly using particle swarms to manipulate and attach components. Future efforts should be directed toward examining the effects of Brownian noise, pose control for multiple-part assembly, trajectory prediction, and manipulation in crowded workspaces.
 In Chapter 4 We assumed friction was sufficient to completely stop particles in contact with the boundary. 
  The algorithms would require retooling to handle small friction coefficients.

### 2018-06-12 Shiva Dissertation/chap/intro.tex
Made few edits and added the new pictures.

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{MicroRobotics.png}
\end{overpic}
\caption{\label{fig:microrobotics} %Controlling a swarm of robots with global inputs. 
Microrobots has the potential to revolutionize medical applications. Used with permission from \cite{nelson2010microrobots}.
}
\end{figure}
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.2\figwid]{first.png}\put(3,97){a)}
\end{overpic}
\begin{overpic}[width =0.2\figwid]{second.png}\put(3,95){b)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{third.png}\put(3,85){c)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{fourth.png}\put(3,85){d)}
\end{overpic}
\caption{\label{fig:model} %Controlling a swarm of robots with global inputs. 
a) The robots are actually simple particles that can be controlled by a global force. b) All the particles get the same control input. c,d) Breaking the symmetry is only possible with external boundary or obstacle.
}
\end{figure}
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection shown in Fig. \ref{fig:microrobotics} \cite{nelson2010microrobots} and 2) ex vivo to assemble structures in parallel. 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads.
 Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group such as mean position and variance. 
 Limited computation and communication at small scales also makes autonomous operation or direct control over individual robots difficult. 
  Instead, this dissertation treats the robots that are steered by a global control signal broadcast to the entire population. 
  The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
 Particle swarms propelled by a uniform field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}. 
% The transportation methodology is similar to that in~\cite{sugawara2014object}, but rather than using onboard computation or sensing, the particles all move in the same direction.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm. Figure \ref{fig:model} shows an example of simple particles when they all get the same control input.
 Techniques are needed that can handle this underactuation.

>>>>

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{MicroRobotics.png}
\end{overpic}
\caption{\label{fig:microrobotics} %Controlling a swarm of robots with global inputs. 
Microrobots has the potential to revolutionize medical applications. Used with permission from \cite{nelson2010microrobots}.
}
\end{figure}
\begin{figure}
\centering
\renewcommand{\figwid}{0.49\columnwidth}
\begin{overpic}[width =\figwid]{physicalPuzzle.pdf}
\end{overpic}
\begin{overpic}[width =\figwid]{physicalDelivery.pdf}
\end{overpic}
\caption{\label{fig:assembly} %Controlling a swarm of robots with global inputs. 
Assembling and delivering different parts of an object using a swarm of simple robots.
}
\end{figure}

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.2\figwid]{first.png}\put(3,97){a)}
\end{overpic}
\begin{overpic}[width =0.2\figwid]{second.png}\put(3,95){b)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{third.png}\put(3,85){c)}
\end{overpic}
\begin{overpic}[width =0.25\figwid]{fourth.png}\put(3,85){d)}
\end{overpic}
\caption{\label{fig:model} %Controlling a swarm of robots with global inputs. 
a) The robots are actually simple particles that can be controlled by a global force. b) All the particles get the same control input. c,d) Breaking the symmetry is only possible with external boundary or obstacle.
}
\end{figure}
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Our vision is for large swarms of robots to be remotely guided 1) through the human body, to cure disease, heal tissue, and prevent infection shown in Fig. \ref{fig:microrobotics} \cite{nelson2010microrobots} and 2) ex vivo to assemble structures in parallel shown in Fig. \ref{fig:assembly}. 
 For each application, large numbers of micro robots are required  to deliver sufficient payloads.
 Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group such as mean position and variance. 
 Limited computation and communication at small scales also makes autonomous operation or direct control over individual robots difficult. 
  Instead, this dissertation treats the robots that are steered by a global control signal broadcast to the entire population. 
  The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
 Particle swarms propelled by a uniform field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}. 
% The transportation methodology is similar to that in~\cite{sugawara2014object}, but rather than using onboard computation or sensing, the particles all move in the same direction.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm. Figure \ref{fig:model} shows an example of simple particles when they all get the same control input.
 Techniques are needed that can handle this underactuation.

### 2018-06-12 Shiva Dissertation/chap3/theory.tex
Still requires some edits.
Made few edits and added the new pictures.

%pivoted comparisons:
\begin{figure*}
\centering
%\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width=0.4\columnwidth]{PivotDrawing.pdf}
\end{overpic}\\
\begin{overpic}[width =0.75\columnwidth]{BestLocationPivot.pdf}%\put(1,55){a)}
\end{overpic} 
\begin{overpic}[width =0.61\columnwidth]{MaxTorquePivot.pdf}%\put(1,55){a)}
\end{overpic}
%\vspace{-0.5em}
\caption{\label{fig:bestLoc} Best location to push and maximum torque plots for a pivoted object of length 1, pivoted at 0. Generating code is in the attachment.
%\vspace{-2em}
}
\end{figure*}

@@

%free torque comparison
\begin{figure*}
\centering
%\renewcommand{\figwid}{0.49\columnwidth}
\begin{overpic}[width =0.4\columnwidth]{FreeDrawing.pdf}
\end{overpic}\\
\begin{overpic}[width =0.75\columnwidth]{TorqueFreeBestPush.pdf}
\end{overpic}
\begin{overpic}[width =0.61\columnwidth]{TorqueFreeComparison.pdf}
\end{overpic}
%\vspace{-0.5em}
\caption{\label{fig:maxTorque} Best location to push and maximum torque plots for a free object of length 2, located from $x=-1$ to $1$.
%\vspace{-2em}
}
\end{figure*}

@@

\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.6\figwid]{AngleOfRepose.pdf}%\put(1,55){a)}
\end{overpic}\\
\vspace{0.5em}
\begin{overpic}[width =0.6\figwid]{AngleOfReposeForce.pdf}%\put(1,55){a)}
\end{overpic}\\
\vspace{0.5em}
\begin{overpic}[width =0.6\figwid]{AngleOfReposeTorque.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:AngleOfReposeForce} Top plot shows colored particulate heaped up on pink-colored long rods. 
%Particulate is moving in the $-y$ direction, and the rods are tilted at $\theta=\{-45,-22.5,0,22.5,45\}^\circ$ with respect to the $x$ axis. 
% A thin gray line extends upwards from the rod COM, showing how more particulate is heaped on the right side of the rod for positive $\theta$ and more on the left side for negative $\theta$. 
%  This uneven particulate generates a restoring torque. 
 Middle plot shows the force applied to the rod and bottom the torque as a function of $\theta$ for four angle of repose values.
 %The rod length $\ell=1$. 
   The maximum torque values are shown with black dots.
% Generating code is in the attachment. 
%\vspace{-2em}
}
\end{figure}

Consider a swarm of granular particles applying force to a rod. 
If the rod moves slower than the particles, these particles will build up behind the rod in a characteristic triangular shape defined by an apex angle. This piling up is common to all granular media, and the angle formed is a function of the \emph{angle of repose}.% for the media, see \cite{angleofRepose}.
By measuring the angle of repose for the particles shown in the top plot of Fig.~\ref{fig:AngleOfReposeForce}, we can estimate the force and torque that the swarm is applying to the rod as a function of the rod's length, the angle of repose, and orientation of the rod.
 We define the angle of repose as $\alpha$, the rod's orientation relative to 90$^\circ$ from the particle movement vector as $\theta$, and the rod's length as $\ell$. 
By integrating over the triangular shape, the force applied to the rod (when a unit area of particles produces 1 N of force) is:

>>>>

%pivoted comparisons:
\begin{figure*}
\centering
%\renewcommand{\figwid}{0.66\columnwidth}
%\hbox{\hspace{-0.5em} \includegraphics[scale=0.6]{bar}}
\begin{overpic}[width=0.4\columnwidth]{PivotDrawing.pdf}
\end{overpic}\\
\begin{overpic}[width =0.75\columnwidth]{BestLocationPivot.pdf}%\put(1,55){a)}
\end{overpic} 
\hbox{\hspace{1.5em} \begin{overpic}[width =0.68\columnwidth]{MaxTorquePivot.pdf}%\put(1,55){a)}
\end{overpic}}
%\vspace{-0.5em}
\caption{\label{fig:bestLoc} Best location to push and maximum torque plots for a pivoted object of length 1, pivoted at 0. Generating code is in the attachment.
%\vspace{-2em}
}
\end{figure*}

@@

%free torque comparison
\begin{figure*}
\begin{center}
%\renewcommand{\figwid}{0.49\columnwidth}
\begin{overpic}[width =0.4\columnwidth]{FreeDrawing.pdf}
\end{overpic}\\
\begin{overpic}[width =0.75\columnwidth]{TorqueFreeBestPush.pdf}
\end{overpic}
\hbox{\hspace{1.75em}\begin{overpic}[width =0.68\columnwidth]{TorqueFreeComparison.pdf}
\end{overpic}}

%\vspace{-0.5em}
\caption{\label{fig:maxTorque} Best location to push and maximum torque plots for a free object of length 2, located from $x=-1$ to $1$.
%\vspace{-2em}
}
\end{center}
\end{figure*}

@@

Consider a swarm of granular particles applying force to a rod. 
If the rod moves slower than the particles, these particles will build up behind the rod in a characteristic triangular shape defined by an apex angle. This piling up is common to all granular media, and the angle formed is a function of the \emph{angle of repose}. Three different values of angle of repose is shown in Fig.~\ref{fig:angle}. The center of mass of the rod is in the middle of the rod, but center of mass of the granular particles changes for different values of angle of repose. % for the media, see \cite{angleofRepose}.
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{Angle.pdf}%\put(1,55){a)}
\end{overpic}
\caption{\label{fig:Angle} Different values of angle of repose is shown when granular particles move faster than the rod.
}
\end{figure}

By measuring the angle of repose for the particles shown in the top plot of Fig.~\ref{fig:AngleOfReposeForce}, we can estimate the force and torque that the swarm is applying to the rod as a function of the rod's length, the angle of repose, and orientation of the rod.
 We define the angle of repose as $\alpha$, the rod's orientation relative to 90$^\circ$ from the particle movement vector as $\theta$, and the rod's length as $\ell$. 
By integrating over the triangular shape, the force applied to the rod (when a unit area of particles produces 1 N of force) is:
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =0.6\figwid]{AngleOfRepose.pdf}%\put(1,55){a)}
\end{overpic}\\
\vspace{0.5em}
\begin{overpic}[width =0.6\figwid]{AngleOfReposeForce.pdf}%\put(1,55){a)}
\end{overpic}\\
\vspace{0.5em}
\begin{overpic}[width =0.6\figwid]{AngleOfReposeTorque.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:AngleOfReposeForce} Top plot shows colored particulate heaped up on pink-colored long rods. 
%Particulate is moving in the $-y$ direction, and the rods are tilted at $\theta=\{-45,-22.5,0,22.5,45\}^\circ$ with respect to the $x$ axis. 
% A thin gray line extends upwards from the rod COM, showing how more particulate is heaped on the right side of the rod for positive $\theta$ and more on the left side for negative $\theta$. 
%  This uneven particulate generates a restoring torque. 
 Middle plot shows the force applied to the rod and bottom the torque as a function of $\theta$ for four angle of repose values.
 %The rod length $\ell=1$. 
   The maximum torque values are shown with black dots.
% Generating code is in the attachment. 
%\vspace{-2em}
}
\end{figure}
